%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{csaund-resume}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated March 20, 2017

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Carolyn}{Saund}{ \urlstyle{same}\href{http://carolynsaund.me}{carolynsaund.me}\\
\href{mailto:carolyn.saund@gmail.com}{carolyn.saund@gmail.com} | 650.483.4727
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Tufts University}
\descript{BSc in Computer Science, Brain and Cognitive Science}
\location{May 2015 | Somerville, MA}
\location{ Cum. GPA: 3.46 / 4.0 \\
Major GPA: 3.8 / 4.0}
\sectionsep

\subsection{University of Canterbury}
\descript{BS in Computer Science}
\location{June 2013 - Jan 2014 | Christchurch, NZ}
College of Engineering \\
\location{ Cum. GPA: 4.0 / 4.0 } 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/csaund}{\bf csaund} \\
LinkedIn://  \href{https://www.linkedin.com/in/carolynsaund}{\bf carolynsaund} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Advanced Topics in Machine Learning \\
Computational Models of Cognitive Science \\
Stochastic Systems \\
Linear Algebra \\
Machine Architecture and Assembly \\
Advanced Topics in Artificial Intelligence \\
Programming Languages \\
Computational Theory \\
\sectionsep

\subsection{Continuing - Technical}
Advanced Seminar in Cognitive Architectures \\
Neural Networks for Machine Learning \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
\location{Over 5000 lines:}
Javascript \textbullet{} Python \textbullet{} C \\
C++ \\
\location{Over 500 lines:}
LISP \textbullet{} \textbullet{} CSS \textbullet{} HTTP \\
\location{Familiar:}
Golang \textbullet{} LaTeX \textbullet{} MySQL
\subsection{Workflow/Frameworks}
git/github \textbullet{} NodeJS/React \textbullet{} SVN \textbullet{} \\
 Unix/Linux \textbullet{} Jenkins/TDD \textbullet{} CI releases
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Jibo Inc.} \\
\descript{Robot SDK Engineer }
\location{May 2015 - Dec 2016 | Boston, MA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Employee 20, first hire of SDK team.
\item Architected data APIs for dev tools to manage robot sensory input (cameras/mics).
\item Won first company culture award for "outstanding cultural contributions."
\item 20+ public speaking appearances for SDK evangelist, including SXSW and WECode."
\end{tightemize}
\descript{Character AI Engineer }
\location{Jan 2017 - Present | Boston, MA}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Designed and implemented robotic Emotion System and corresponding impacts on robot behavior.
\end{tightemize}
\sectionsep

\runsubsection{Spotify}
\descript{| Software Engineering Intern }
\location{May 2014 - Sep 2014 | NY, NY}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Full stack development of internal desktop application.
\item Developed new web tools to improve internal testing and data collection.
\item Worked on team to test and implement new song recommendation algorithm.
\end{tightemize}
\sectionsep

\runsubsection{Tufts University}
\descript{| Teaching Assistant, Computer Science }
\location{Jan 2012 - Jan 2015 | Somerville, MA}
\begin{tightemize}
\item Data Structures, Machine Architecture, Machine Learning
\item Taught theory and laboratory skills to students with wide range of abilities.
\item Participated in designing course structure and syllabus.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Leadership and Community Service}
\runsubsection{Girls Who Code}
\descript{| Instructor}
\location{Sept 2015 - Jan 2016 | Belmont, MA}
Instructed three levels of middle- and high-school aged students from introduction to basic data strcutures. Supplemented given course materials with additional lesson plans to emphasize CS fundamentals.
\sectionsep

\runsubsection{Women in Computer Science}
\descript{| President}
\location{Jan 2013 - Jan 2015 | Somerville, MA}
\begin{tightemize}
\item Coordinated logistics of club hackathons, speakers, and outreach.
\item Led executive board in creating WiCS mission and club constitution.
\item Gained University recognition and sponsorship and widespread campus presence.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Other Extracurriculars}
\begin{tabular}{rll}
 Girl Scouts Gold Award \textbullet{} Project Management and Leadership Book Group \\
 \textbullet{} Tufts Mountain Club Trip Coordinator \textbullet{} WWOOF Worker (Germany) \\ 
 \textbullet{} Ultimate Frisbee Captain \textbullet{} Alpha Omicron Pi (VP Academic Development) \\
 \textbullet{} 20+ countries visited
\end{tabular}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
