
\documentclass[]{csaund_resume-openfont}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated September 17, 2018

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Carolyn}{Saund}{ \urlstyle{same}\href{http://carolynsaund.me}{carolynsaund.me} \\
\href{mailto:carolyn.saund@gmail.com}{carolyn.saund@gmail.com} | +44.759.557.9616
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.30\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Tufts University}
\descript{BSc in Computer Science, Brain and Cognitive Science}
\location{May 2015 | Somerville, MA}
\sectionsep

\subsection{University of Canterbury}
\descript{BS in Computer Science}
\location{June 2013 - Jan 2014 | Christchurch, NZ}
College of Engineering \\
\location{ GPA: 4.0 / 4.0 } 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Advanced Topics in Machine Learning \\
Computational Models of Cognitive Science \\
Stochastic Systems \\
Linear Algebra \\
Machine Architecture and Assembly \\
Advanced Topics in Artificial Intelligence \\
Programming Languages \\
Computational Theory \\
\sectionsep

\subsection{Continuing}
Advanced Seminar in Cognitive Architectures \\
Neural Networks for Machine Learning 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
\location{Over 5000 lines:}
Javascript \textbullet{} Python \textbullet{} C \\
C++ \textbullet{} Java  \\
\location{Over 500 lines:}
LISP \textbullet{} CSS \textbullet{} HTTP \textbullet{} R \\
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\subsection{Workflow/Frameworks}
git/github \textbullet{} NodeJS  \textbullet{} React \textbullet{} SVN \textbullet{} \\
 Unix/Linux \textbullet{} Jenkins/TDD \textbullet{} CI releases \\
 Stash \textbullet{} Phabricator/arcanist \textbullet{} Gradle \\
 MongoDB \textbullet{} Electron 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Cogito} \\

\descript{Platform Team Lead}
\location{Jan 2018 - August 2018 | Boston MA}
\vspace{\topsep} %
\begin{tightemize}
\item Managed Agile team of 10 engineers 
\item Oversaw top-to-bottom implementation of three major user-facing features
\end{tightemize}

\descript{Senior Software Developer }
\location{August 2017 - Jan 2018 | Boston MA}
\begin{tightemize}
\item Originally Implemented and manage release pipeline.
\item Full-stack development of Role-Based User Management (RBUM) APIs.
\end{tightemize}
\sectionsep

\runsubsection{Jibo} \\
\descript{Robot SDK Engineer }
\location{May 2015 - Dec 2016 | Boston, MA}
\begin{tightemize}
\item Employee 20(/110) Designed a series of tutorials from "Getting Started" to advanced usage still used to onboard internal and external developers.
\item Architected data APIs for dev tools to manage robot sensory input from cameras and microphones.
\item Implemented frontend UI and developer interfaces to build high-level skills.
\item Won first company culture award for "outstanding cultural contributions."
\end{tightemize}
\descript{Character AI Engineer }
\location{Jan 2017 - August 2017 | Boston, MA}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Designed and implemented robotic bi-axial Emotion System and corresponding impacts on robot behavior.
\item Single-handedly architected and maintained robot listening pipeline (main interface for interaction).
\end{tightemize}
\descript{ Software Consultant }
\location{August 2017 - Present | Boston, MA}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Continuing work to rearchitect APIs in cloud-based architecture
\end{tightemize}
\sectionsep

\runsubsection{Spotify} \\
\descript{Software Engineering Intern }
\location{May 2014 - Sep 2014 | NY, NY}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Full stack development of internal desktop application.
\item Developed web APIs and GUI for music annotation tools
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Public Speaking and Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Drosophila}
\begin{tightemize}
\item Designed and programmed arduino "badge" with  genetic algorithms for LED display to recombine when near another badge.
\end{tightemize}
\sectionsep
\runsubsection{The Neuron}
\begin{tightemize}
\item Programmed LED strips around metal sculpture to respond based on microphone input, compute audio intensity threshold, and "fire" another LED strip with enough sound intensity.
\end{tightemize}
\sectionsep

\end{minipage}

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Community Service
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Leadership and Community Service}
\runsubsection{Cambridge Inventors Club}
\descript{| Volunteer}
\location{Jan 2016 - Present | Cambridge, MA}
Work with children age 8-13 on engineering fundamentals, such as iterative design, retrospectives, and cooperation
\sectionsep

\runsubsection{Boston Ultimate Disk Alliance}
\descript{| Coach}
\location{March 2016 - Sept 2016 | Jamaica Plain, MA}
First coach on new high school girls team, focused on empowering women in the Boston ultimate community
\sectionsep

\runsubsection{Girls Who Code}
\descript{| Instructor}
\location{Sept 2015 - June 2016 | Belmont, MA}
Instructed three levels of middle- and high-school aged students from introduction to basic data strcutures. Supplemented given course materials with additional lesson plans to emphasize CS fundamentals.
\sectionsep

\runsubsection{Women in Computer Science}
\descript{| President}
\location{Jan 2013 - Jan 2015 | Somerville, MA}
\begin{tightemize}
\item Coordinated logistics of club hackathons, speakers, and outreach.
\item Led executive board in creating WiCS mission and club constitution.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Other Extracurriculars and Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extracurriculars}
\runsubsection{Awards}
\descript{ }
\begin{tightemize}
\item Culture Award (First Recipient) | Jibo Inc. Award for outstanding cultural contributions to the company.
\item Girl Scout Gold Award | Highest Honor of Girl Scouts of America
\end{tightemize}
\sectionsep

\runsubsection{Public Speaking Appearances}
\descript {}
\begin{tightemize}
\item SXSW, Robot Petting Zoo (presentation \& booth)
\item Women Engineers who Code Conference, (technical workshop \& imposter syndrome seminar)
\item Lesbians Who Tech, presentation on emotional future of robotics 
\item Boston ML Meetup, presenter on Innovations in Human-Computer Interfaces
\item MLHack Championships, (technical presentation \& hackathon judge)
\item Tufts WICS Conference, Alumni Pannel 
\end{tightemize}
\sectionsep

\runsubsection{Memberships \& Activities}
\descript{ }
\location{Current}
\begin{tightemize}
\item Cognitive Science Society
\item Project Management and Leadership Book Group 
\item AI and Technological Futurism Book Group (Organizer)
\item Div II Ultimate Frisbee (Captain)
\end{tightemize}
\location{Former (Undergraduate)}
\begin{tightemize}
\item Vice President of Academic Development, Alpha Omicron Pi
\item Tufts Mountain Club, Trip Coordinator
\item Midnight Judges Jazz Combo
\end{tightemize}
\location{Misc.}
\begin{tightemize}
\item 20+ countries visited
\item WWOOF Worker (Germany)
\item Avid century bike-rider and marathoner
\end{tightemize}
\sectionsep

\end{document}  \documentclass[]{article}
